Closed-loop Neuromorphic Benchmarks

### 2015-10-01 paper/paper.tex
Tweaked captions for figs 4,5,6

While the primary purpose of this paper is in decribing the benchmarking
methodology, it is also worth noting that these benchmarks indicate
that the neuromorphic learning rule under investigation here is extremely robost.  As
shown in \ref{fig:analysis_neurons_cpu}, even just 500 neurons can consistently
adapt to control a \emph{randomly generated} 15-joint body simulation, and
deal with larger delays and noise than were seen in the example 1-joint
physical embodiment.  Since this learning system is robust across such a
wide range of conditions, and since it is efficiently implementable in a
wide variety of neuromorohic hardware, we feel it is worth further study.  This must include 
both a wider variety of minimal simulation benchmarks and also a few more 
traditional benchmarks.  These traditional
benchmarks would be particular real physical systems (specific robot arms,
for example), but testing on those would only reveal performance on those
particular arms.  As we argued here, benchmarking against a wide variety of 
randomly generated minimal simulation systems is needed to demonstrate the
space of potential situations in which neuromorphic adaptive control performs well.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_basic}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_basic} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems.
     Each system is running 500 neurons.  The hardware do not statistically
     significantly differ, and are all clear improvements over the having
     no adaptation at all.
     Scatterplots show individual runs, the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_compute}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_compute} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of in real time.  Scatterplots show individual runs, the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  In this case,
     all three hardware systems perform equally well.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_power}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_power} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of per 0.1 Watt of power consumption.  Scatterplots show individual runs, the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  The SpiNNaker system is a statistically
 significant improvement over the other two.}
\end{figure}

>>>>

While the primary purpose of this paper is in decribing the benchmarking
methodology, it is also worth noting that these benchmarks indicate
that the neuromorphic learning rule under investigation here is extremely robost.  As
shown in Figure \ref{fig:analysis_neurons_cpu}, even just 500 neurons can consistently
adapt to control a \emph{randomly generated} 15-joint body simulation, and
deal with larger delays and noise than were seen in the example 1-joint
physical embodiment.  Since this learning system is robust across such a
wide range of conditions, and since it is efficiently implementable in a
wide variety of neuromorohic hardware, we feel it is worth further study.  This must include 
both a wider variety of minimal simulation benchmarks and also a few more 
traditional benchmarks.  These traditional
benchmarks would be particular real physical systems (specific robot arms,
for example), but testing on those would only reveal performance on those
particular arms.  As we argued here, benchmarking against a wide variety of 
randomly generated minimal simulation systems is needed to demonstrate the
space of potential situations in which neuromorphic adaptive control performs well.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_basic}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_basic} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems.
     Each system is running 500 neurons.  The hardware do not statistically
     significantly differ, but are all statistically significant improvements 
     over no adaptation (p<0.05).
     Scatterplots show individual runs (with random jitter on the x-axis
     to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_compute}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_compute} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of in real time.  Scatterplots show individual runs (with random
     jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  In this case,
 there is no statistical difference between the three hardware systems (p>0.05).}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_power}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_power} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of per 0.1 Watt of power consumption.  Scatterplots show individual runs (with random jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  The SpiNNaker system is a statistically
 significant improvement over the other two (p<0.05).}
\end{figure}
